### 2024-04-10 paper/paper.qmd
added graphs for volatility, started paper, updated refs

---
title: "Precious Metals Or Crypto, Where Should I Invest?"
subtitle: "A Historical Analysis of the Two Major Asset Categories 2017-Present"
author: 
  - Yi Fei Pang
thanks: "Code and data are available at: https://github.com/apang00/investment-comparison"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: ""
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(here)
library(knitr)
library(readr)
library(ggplot2)
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-04-10 scripts/02-data_cleaning.R

@@ -11,19 +11,21 @@ library(tidyverse)
 library(dplyr)
 library(haven)
 library(here)
+library(TTR)
 
 #### Clean data ####
-
-# In this category I will set 1 btc as the standard on the graph and try to 
-# match the other values to be in the 1 btc vicinity.
-# For closing prices, I will round to the nearest integer and for dates, I will
-# select the fist and 15th of every month starting 2017-11-15 and ending with
-# 2024-04-01
 
 eth <- read_csv(here::here("data/raw_data/ETH-USD.csv"))
 btc <- read_csv(here::here("data/raw_data/BTC-USD.csv"))
 silver <- read_csv(here::here("data/raw_data/silver.csv"))
 gold <- read_csv(here::here("data/raw_data/gold.csv"))
+
+## Section 1 ## 
+# In this category I will set 1 btc as the standard on the graph and try to 
+# match the other values to be in the 1 btc vicinity.
+# For closing prices, I will round to the nearest integer and for dates, I will
+# select the fist and 15th of every month starting 2017-11-15 and ending with
+# 2024-04-01
 
 # I am doing 20x for eth to match btc
 eth_clean <- eth %>%
@@ -49,12 +51,12 @@ gold_clean <- gold %>%
   filter(Date >= "2017-11-14") %>%
   rename(gold_Close = Close)
 
-# 2000 oz of silver to match btc
+# 2500 oz of silver to match btc
 silver_clean <- silver %>%
   mutate(Date = as.Date(Date, format = "%m/%d/%y"), 
          Date = format(Date, "%Y-%m-%d")) %>% 
   select(Close, Date) %>%
-  mutate(Close = round(Close * 2000, 0)) %>%
+  mutate(Close = round(Close * 2500, 0)) %>%
   filter(substr(Date, 9, 10) %in% c("01", "15")) %>%
   filter(Date >= "2017-11-14") %>%
   rename(silver_Close = Close)
@@ -65,6 +67,104 @@ metals <- inner_join(gold_clean, silver_clean, by = "Date")
 metals <- metals %>%
   select(Date, everything())
 
+## Section 2 ##
+# this section I will look at the Average True Range of each asset after 
+# normalization
+
[…]

### 2024-04-10 scripts/03-test_data.R

@@ -12,8 +12,10 @@ library(tidyverse)
 
 
 #### Test data ####
-crypto <- read_csv(here::here("data/analysis_data/crypto.csv"))
-metals <- read_csv(here::here("data/analysis_data/metals.csv"))
+crypto <- read_csv(here::here("data/analysis_data/crypto prices.csv"))
+metals <- read_csv(here::here("data/analysis_data/metals prices.csv"))
+cryptov <- read_csv(here::here("data/analysis_data/crypto volatility.csv"))
+metalsv <- read_csv(here::here("data/analysis_data/metals volatility.csv"))
 
 # Test that years exist between 2017 to 2024
 all(as.numeric(format(crypto$Date, "%Y")) %in% 2017:2024)
@@ -23,8 +25,12 @@ all(as.numeric(format(metals$Date, "%Y")) %in% 2017:2024)
 all(format(crypto$Date, "%d") %in% c("01", "15"))
 all(format(metals$Date, "%d") %in% c("01", "15"))
 
-# Test for range of values, to account for potential typos or data misinput
+# Test for range of values, to account for potential typos or data misinputs
 !any(crypto$eth_Close > 100000) && !any(crypto$eth_Close < 500)
 !any(crypto$btc_Close > 100000) && !any(crypto$btc_Close < 2000)
 !any(metals$gold_Close > 100000) && !any(metals$gold_Close < 20000)
 !any(metals$silver_Close > 100000) && !any(metals$silver_Close < 20000)
+
+# Testing for any lines that are blanks
+!any(is.na(cryptov)) 
+!any(is.na(metalsv)) 

### 2024-04-10 scripts/04-model.R

@@ -12,8 +12,11 @@ library(rstanarm)
 library(ggplot2)
 
 #### Read data ####
-crypto <- read_csv(here::here("data/analysis_data/crypto.csv"))
-metals <- read_csv(here::here("data/analysis_data/metals.csv"))
+crypto <- read_csv(here::here("data/analysis_data/crypto prices.csv"))
+metals <- read_csv(here::here("data/analysis_data/metals prices.csv"))
+cryptov <- read_csv(here::here("data/analysis_data/crypto volatility.csv"))
+metalsv <- read_csv(here::here("data/analysis_data/metals volatility.csv"))
+
 
 ### Model data ####
 compilation <- ggplot() +
@@ -24,28 +27,34 @@ compilation <- ggplot() +
   labs(title = "Asset Comparisons 2017 to Present",
        x = "Date", y = "Closing Amount ($USD)") +
   scale_color_manual(values = c("Ethereum" = "royalblue", "Bitcoin" = "sienna2", "Gold" = "#FFD700", "Silver" = "#C0C0C0"),
-                     labels = c("Ethereum" = "Ethereum (20 Units)", "Bitcoin" = "Bitcoin", "Gold" = "Gold (30 oz.)", "Silver" = "Silver (2000 oz.)")) +
+                     labels = c("Ethereum" = "Ethereum (20 Units)", "Bitcoin" = "Bitcoin", "Gold" = "Gold (30 oz.)", "Silver" = "Silver (2500 oz.)")) +
   guides(color = guide_legend(title = "Assets")) +  
   scale_x_date(date_breaks = "1 year", date_labels = "%Y")
-  
 
-"
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )"
+compilation
+
+volatility <- ggplot() +
+  geom_line(data = cryptov, aes(x = Date, y = eth_ATR_norm, color = "Ethereum"), size = 0.75) +
+  geom_line(data = cryptov, aes(x = Date, y = btc_ATR_norm, color = "Bitcoin"), size = 0.75) +
[…]

### 2024-04-12 paper/paper.qmd
slight changes to qmd file

@@
 date-format: "D MMMM YYYY"
+toc: true
 format: 
@@
     geometry: margin = 1in
-    abstract: ""
+    abstract: "This paper utilizes and compares datasets extracted from Yahoo Finance and Business insider to perform a financial analysis.
+The analysis indicates a negative correlation in relation to economic health and precious metal and crpto rates.
+Furthermore, it shows the growth of crytpo as an asset has been much stronger than precious metals.
+The importance of this analysis can be very beneficial today especially since there is a recession happening."
 number-sections: true
@@
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
 ```
@@
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
@@
 first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+  readRDS(file = here::here("models/price chart.rds"))
 ```
@@
 ```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
@@
 ```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```
@@
 ```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-04-16 paper/paper.qmd
changes to qmd

@@
 
+{{< pagebreak >}}
 # Introduction
 
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
+Throughout history, human currency has always been evolving alongside out civilization.
+From the archaic days of the bartering systems where people traded raw materials, coins and precious metals emerged, then came paper money.
+As humans evolved even further, electronic banking with credit card emerged and now finally, crytpocurrencies.
+At every stage of society, humans have tied a value on an economic instrument as a way of wealth storage and wealth exchange.
 
-The remainder of this paper is structured as follows. @sec-data....
+Gold and silver has been an asset since the ancient civilizations of Egyptians and Incas.
+Both metals are malleable and therefore can easily be stamped into coins or molded into jewelry.
+Furthermore, pure gold and silver does not corrode or tarnish, thus making them timeless assets [@InvestopediaMetals].
+Thousands of years later, in our modern era, gold and silver still remain as solid assets because of their durability, liquidity, and stability.
+
+However, in the recent years, a new asset has emerged and that is cryptocurrencies.
+Originally developed as a method of making untraceable transactions, this technology has quickly gained popularity and has transformed into more of an investment rather than a currency.
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+## Data Description
+
+This paper uses four separated datasets from two different sources.
+The gold  [@goldbusinessinsider] and silver [@silverbusinessinsider] raw datasets were sourced from a subsidiary of Business Insider, Market Insider.
+These two datasets include detailed financial information regarding gold and silver data starting from late 2017 until present.
+The other two cryptocurrency datasets for Ethereum [@ethyahoofinance] and Bitcoin [@btcyahoofinance] come from Yahoo Finance also ranging from late 2017 until present.
+All four datasets include details such as daily open and closing prices as well as high/lows and volume data.
+In addition, all data is marked in US dollars.
+The data is sourced from live charts for the daily open, close, and volume recorded on exchanges and recorded at the end of every day.
+The cleaning, modelling, and analysis of these four datasets will be carried out using the statistical programming language `R` [@citeR], using the packages `tidyverse`[@citetidy], `here`[@citeHere], `rstanarm`[@rstanarm], `dplyr` (Wickham et al.
+2021), and `ggplot2`[@citeGG].
 
 ```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+library(tidyverse)
+library(here)
+library(knitr)
+
+price <- read_csv(here::here("data/analysis_data/crypto prices.csv"))
+volatility <- read_csv(here::here("data/analysis_data/crypto volatility.csv"))
+p_5 <- head(price, 5)
+v_5 <- head(volatility, 5)
 
@@
 
-Talk more about it.
+## Price Data
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+The crypto prices and metals prices cleaned datasets feature the closing price points of the two cryptocurrencies eth_Close, btc_Close, along with the respective close prices for the metals gold_Close and silver_Close.
+In addition, there is a date column for the closing prices.
+These datasets range from November 12, 2017 until the date they were fetched, April 4th, 2024.
+Though there is data for every single day of the year, within the aforementioned range, the cleaned dataset only takes into account the closing balance of the crytpocurrency/precious metal every 15 days, or the 1st and 15th of every month.
+The purpose of that is to reduce noise and filters out short term volatility and gives the data a more long term perspective.
+In addition to the date adjustment, there are also adjustments made to the closing prices.
+For readability in graphs, all assets were readjusted to have a present value of in the range of 1 Bitcoin.
+The adjustments made were 20x Ethereum, 30x Gold (oz.), and 2500x Silver (oz.).
 
 ```{r}
+#| echo: false
+#| warning: false
+#| label: tbl-1
+#| tbl-cap: "A summary table for crypto price data"
+
+kable(p_5)
+```
+
+## Volatility Data
+
+The volatility data was separated much like the prices datasets.
+One dataset for crypto volatility and one for metals volatility.
+In both datasets, volatility was calculated by using a normalized average true range.
+
+First, the true range was calculated with:
+
+TR = Max [(H - L), |H - Cp|, |L - Cp|]
+
+Where:
+H = Today's high
+L = Today's low
+Cp = Yesterday's closing price
+Max = Highest value of the three terms
+Source: [@InvestopediaFormula]
+
+Then the average true range was calculated with and represented by (asset)_ATR in @tbl-2:
+
+(1/n) * Σ(TRi)
+
+Where:
+TRi = Particular true range for each period (e.g., first day's TR, second day's TR, etc.)
+Σ = Summation symbol (summing up all the individual TRi values)
+n = Number of periods (15 in the data to match the price data)
+Source: [@InvestopediaFormula]
+
+The normalized average true range was calculated by normalizing the ATR value with the closing price of the asset and represented by (asset)_ATR_norm in @tbl-2:
+
+ATR/Cp
+
+Where: 
+ATR = The ATR of the asset 
+Cp = Current day's closing price
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: tbl-2
+#| tbl-cap: "A summary table for crypto volatility"
+
+kable(v_5)
 
 ```
-
-Talk way more about it.
 
@@
 
-## First discussion point {#sec-first-point}
+##
 
@@
 
-## Third discussion point
+## Biases and Weaknesses
+One of the greatest weaknesses stems from the limited historical data of cryptocurrencies.
+The value of precious metals can be trace back centuries and has solidified itself as a solid holding asset while cryptocurrencies such as Ethereum was only introduced in the late 2016s.
+Therefore, the only results and conclusion that can be made...
 
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
+## Next Steps
+Some next steps I can take for future devlopments can be to continue to monitor the price of crypto over the next few decades and see how it reacts to different economic coniditions and how that compares to precious metals.
 

### 2024-04-16 scripts/02-data_cleaning.R

@@ -29,13 +29,13 @@ gold <- read_csv(here::here("data/raw_data/gold.csv"))
 
 # I am doing 20x for eth to match btc
 eth_clean <- eth %>%
-  select(Date, Close, Volume) %>%
+  select(Date, Close) %>%
   mutate(Close = round(Close * 20, 0)) %>%
   filter(substr(Date, 9, 10) %in% c("01", "15")) %>%
   rename(eth_Close = Close)
 
 btc_clean <- btc %>%
-  select(Date, Close, Volume) %>%
+  select(Date, Close) %>%
   mutate(Close = round(Close, 0)) %>%
   filter(substr(Date, 9, 10) %in% c("01", "15")) %>%
   filter(Date >= "2017-11-14") %>%
@@ -62,7 +62,7 @@ silver_clean <- silver %>%
   rename(silver_Close = Close)
 
 # join the 4 datasets into 2, one for crypto one for metals
-crypto <- inner_join(eth_clean, btc_clean, by = "Date")
+crypto <- inner_join(eth_clean, btc_clean, by = "Date") 
 metals <- inner_join(gold_clean, silver_clean, by = "Date")
 metals <- metals %>%
   select(Date, everything())

### 2024-04-16 paper/paper.qmd
added regression data

@@
   - Yi Fei Pang
-thanks: "Code and data are available at: https://github.com/apang00/investment-comparison"
+thanks: "Code and data supporting this analysis is available at: https://github.com/apang00/investment-comparison"
 date: "`r Sys.time()`"
@@
     geometry: margin = 1in
-    abstract: "This paper utilizes and compares datasets extracted from Yahoo Finance and Business insider to perform a financial analysis.
-The analysis indicates a negative correlation in relation to economic health and precious metal and crpto rates.
-Furthermore, it shows the growth of crytpo as an asset has been much stronger than precious metals.
-The importance of this analysis can be very beneficial today especially since there is a recession happening."
+    abstract: "This paper utilizes and compares datasets of the two most held precious metals and the two most held cryptocurrencies.
+A few simple price analyses were implemented to determine which assets were more profitable along with range formulas to determine volatility.
+Observations show that in the recent years, crypto has been a much more profitable investment.
+However, precious metals are much less volatile and consistent.
+The importance of this analysis can be very beneficial today due to the economic turmoil and investors asking: Do I want an asset that's profitable, consistent, or both?"
 number-sections: true
@@
 
-Throughout history, human currency has always been evolving alongside out civilization.
+Throughout history, human currency has always been evolving alongside our civilization.
 From the archaic days of the bartering systems where people traded raw materials, coins and precious metals emerged, then came paper money.
@@
 Furthermore, pure gold and silver does not corrode or tarnish, thus making them timeless assets [@InvestopediaMetals].
-Thousands of years later, in our modern era, gold and silver still remain as solid assets because of their durability, liquidity, and stability.
+Thousands of years later, in our modern era, gold and silver still remain as solid assets because of their durability, liquidity, and stability.Through economic turmoil, precious metals have proven to be an asset that not only holds it's value but has been significantly outperforming the stock markets since the turn of the millennium [@Forbes].In the recent decade, a new category of asset has emerged and performed tremendously well.That is the cryptocurrency.
+Originally developed as a method of making untraceable transactions and used almost exclusively by the Dark Web crowd, this technology has quickly gained popularity and has transformed into more of an investment rather than to obfuscate transactions.
+Cryptocurrencies such as Bitcoin and Ethereum has seen growths of ~20,000% and ~35,000% respectively at their peaks.
 
-However, in the recent years, a new asset has emerged and that is cryptocurrencies.
-Originally developed as a method of making untraceable transactions, this technology has quickly gained popularity and has transformed into more of an investment rather than a currency.
+Since both precious metals and cryptocurrencies have been performing exceptionally well, this paper will analyse asset is a better hold depending on the goal of the investor.
+I will not only focus on the trends for the separate assets through price charts, but also evaluate correlations between the different category of assets through regression.
+Moreover, ranges will be calculated as a method to assess risk and volatility and compared between the two asset categories.
+Overall, it was evident precious metals tend to grow consistently over the year without being significantly affected by the economy or the introduction of other assets.
+In contrast, cryptocurrencies are much more volatile, seeing massive price ranges.
+However, cryptocurrencies tend to grow at much higher rates.
+Over the past decade, both precious metals and cryptocurrencies have been phenomenal assets and looks to continue to rise in value in the foreseeable future.
 
-# Data {#sec-data}
+In the data section of the paper, there will be an introduction regarding where the data came from, and for what period the data was extracted.
+Furthermore, the data cleaning and visualization process will be detailed for creating the price, volatility, and regression charts.
+Next, the model section will explore the linear models used, why they were used, and how they represent the correlations.
+Following that, the results will be discussed includes elements such as the R-square values and p-values.
+To conclude, we will figure out potential weaknesses of the analysis along with the next steps and improvements.
+
+{{< pagebreak >}}
+# Data
 
@@
 All four datasets include details such as daily open and closing prices as well as high/lows and volume data.
-In addition, all data is marked in US dollars.
+In addition, all prices in the data is in US dollars.
 The data is sourced from live charts for the daily open, close, and volume recorded on exchanges and recorded at the end of every day.
@@
 ## Model set-up
+The model will be linear where:
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
 

### 2024-04-16 scripts/02-data_cleaning.R

@@ -12,6 +12,7 @@ library(dplyr)
 library(haven)
 library(here)
 library(TTR)
+library(arrow)
 
 #### Clean data ####
 

### 2024-04-16 scripts/04-model.R

@@ -17,8 +17,12 @@ metals <- read_csv(here::here("data/analysis_data/metals prices.csv"))
 cryptov <- read_csv(here::here("data/analysis_data/crypto volatility.csv"))
 metalsv <- read_csv(here::here("data/analysis_data/metals volatility.csv"))
 
+price_join <- merge(crypto, metals, by = "Date", all = FALSE)
+
 
 ### Model data ####
+
+# Price Data chart
 compilation <- ggplot() +
   geom_line(data = crypto, aes(x = Date, y = eth_Close, color = "Ethereum"), size = 0.75) +
   geom_line(data = crypto, aes(x = Date, y = btc_Close, color = "Bitcoin"), size = 0.75) +
@@ -33,6 +37,7 @@ compilation <- ggplot() +
 
 compilation
 
+# Volatility Data Chart
 volatility <- ggplot() +
   geom_line(data = cryptov, aes(x = Date, y = eth_ATR_norm, color = "Ethereum"), size = 0.75) +
   geom_line(data = cryptov, aes(x = Date, y = btc_ATR_norm, color = "Bitcoin"), size = 0.75) +
@@ -46,6 +51,42 @@ volatility <- ggplot() +
 
 volatility
 
+# Regression Chart BTC-Gold
+bgfit <- lm(gold_Close ~ btc_Close, data = price_join)
+bgplot <- ggplot(price_join, aes(x = btc_Close, y = gold_Close)) +
+  geom_point(color = "blue", size = 2) +
+  geom_abline(intercept = coef(bgfit)[1], slope = coef(bgfit)[2], color = "red") +
+  labs(title = "Bitcoin vs. Gold Prices Regression Model",
+       x = "Bitcoin Closing Price", y = "Gold Closing Price")
+print(bgplot)
+
+# Regression for BTc-Silver
+bsfit <- lm(silver_Close ~ btc_Close, data = price_join)
+bsplot <- ggplot(price_join, aes(x = btc_Close, y = silver_Close)) +
+  geom_point(color = "blue", size = 2) +
+  geom_abline(intercept = coef(bsfit)[1], slope = coef(bsfit)[2], color = "red") +
+  labs(title = "Bitcoin vs. Silver Prices Regression Model",
+       x = "Bitcoin Closing Price", y = "Silver Closing Price")
+print(bsplot)
+
+# Regression for Ethereum-Gold
+egfit <- lm(gold_Close ~ eth_Close, data = price_join)
[…]

### 2024-04-17 paper/paper.qmd
added discussion points

@@
 The gold  [@goldbusinessinsider] and silver [@silverbusinessinsider] raw datasets were sourced from a subsidiary of Business Insider, Market Insider.
-These two datasets include detailed financial information regarding gold and silver data starting from late 2017 until present.
+These two datasets include detailed financial information regarding gold and silver price and volume data starting from late 2017 until present.
 The other two cryptocurrency datasets for Ethereum [@ethyahoofinance] and Bitcoin [@btcyahoofinance] come from Yahoo Finance also ranging from late 2017 until present.
@@
 
-price <- read_csv(here::here("data/analysis_data/crypto prices.csv"))
+crypto <- read_csv(here::here("data/analysis_data/crypto prices.csv"))
+metals <- read_csv(here::here("data/analysis_data/metals prices.csv"))
 volatility <- read_csv(here::here("data/analysis_data/crypto volatility.csv"))
-p_5 <- head(price, 5)
+p_5 <- head(crypto, 5)
+m_5 <- head(metals, 5)
 v_5 <- head(volatility, 5)
@@
 
-The crypto prices and metals prices cleaned datasets feature the closing price points of the two cryptocurrencies eth_Close, btc_Close, along with the respective close prices for the metals gold_Close and silver_Close.
+The crypto prices and metals prices cleaned datasets feature the closing price points of the two cryptocurrencies eth_Close and btc_Close, along with the respective close prices for the metals gold_Close and silver_Close.
 In addition, there is a date column for the closing prices.
 These datasets range from November 12, 2017 until the date they were fetched, April 4th, 2024.
-Though there is data for every single day of the year, within the aforementioned range, the cleaned dataset only takes into account the closing balance of the crytpocurrency/precious metal every 15 days, or the 1st and 15th of every month.
-The purpose of that is to reduce noise and filters out short term volatility and gives the data a more long term perspective.
-In addition to the date adjustment, there are also adjustments made to the closing prices.
-For readability in graphs, all assets were readjusted to have a present value of in the range of 1 Bitcoin.
+Though there is data for every single day of the year within the aforementioned range, the cleaned dataset only takes into account the closing balance of the crytpocurrency/precious metal every 15 days, or the 1st and 15th of every month.
+The purpose is to reduce noise and filters out short term volatility and gives the data a more long term perspective.
+In addition to the date adjustment, there are adjustments made to the closing prices as well.
+For readability in graphs, all assets were readjusted to have a present value of in the vicinity of 1 Bitcoin.
 The adjustments made were 20x Ethereum, 30x Gold (oz.), and 2500x Silver (oz.).
@@
 
+```{r}
+#| echo: false
+#| warning: false
+#| label: tbl-2
+#| tbl-cap: "A summary table for metal price data"
+
+kable(m_5)
+```
+
+{{< pagebreak >}}
 ## Volatility Data
@@
 Where:
+
 H = Today's high
+
 L = Today's low
+
 Cp = Yesterday's closing price
+
 Max = Highest value of the three terms
+
 Source: [@InvestopediaFormula]
 
-Then the average true range was calculated with and represented by (asset)_ATR in @tbl-2:
+__________
+Then the average true range was calculated with and represented by (asset)_ATR in @tbl-3:
 
@@
 TRi = Particular true range for each period (e.g., first day's TR, second day's TR, etc.)
+
 Σ = Summation symbol (summing up all the individual TRi values)
+
 n = Number of periods (15 in the data to match the price data)
+
 Source: [@InvestopediaFormula]
 
-The normalized average true range was calculated by normalizing the ATR value with the closing price of the asset and represented by (asset)_ATR_norm in @tbl-2:
+__________
+In the final step, the normalized average true range was calculated by normalizing the ATR value with the closing price of the asset and represented by (asset)_ATR_norm in @tbl-3:
 
@@
 Where:
+
 ATR = The ATR of the asset
+
 Cp = Current day's closing price
+
+{{< pagebreak >}}
+## Data Visualization
 
@@
 #| warning: false
-#| label: tbl-2
-#| tbl-cap: "A summary table for crypto volatility"
+#| label: fig-1
+#| fig-cap: "Price Comparison All Assets 2017 to Present"
 
-kable(v_5)
+compilation <- ggplot() +
+  geom_line(data = crypto, aes(x = Date, y = eth_Close, color = "Ethereum"), size = 0.75) +
+  geom_line(data = crypto, aes(x = Date, y = btc_Close, color = "Bitcoin"), size = 0.75) +
+  geom_line(data = metals, aes(x = Date, y = gold_Close, color = "Gold"), size = 0.75) +
+  geom_line(data = metals, aes(x = Date, y = silver_Close, color = "Silver"), size = 0.75) +
+  labs(title = "Asset Prices",
+       x = "Date", y = "Closing Amount ($USD)") +
+  scale_color_manual(values = c("Ethereum" = "royalblue", "Bitcoin" = "sienna2", "Gold" = "#FFD700", "Silver" = "#C0C0C0"),
+                     labels = c("Ethereum" = "Ethereum (20 Units)", "Bitcoin" = "Bitcoin", "Gold" = "Gold (30 oz.)", "Silver" = "Silver (2500 oz.)")) +
+  guides(color = guide_legend(title = "Assets")) +  
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y")
 
+compilation
 ```
+The figure above shows the trends of all four separate assets.
+Over the past 7 years, it's evident that all the assets have increased in value significantly.
+Gold tends to have the least fluctuations and grew from close to 38,000 USD per 30 oz.
+to around 66,000 USD.
+Both precious metals are more stable than the cryptos.
+However, both ctyprocurrencies began at less than 10,000 (1 btc and 20 units of eth) and ended up well over 66,000 USD, resulting in a much more drastic return.
 
+{{< pagebreak >}}
 # Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+The goal of my model is to analyse the correlation between crytpo prices and precious metals prices.
+Through observing the previous price chart, there can be a perception of linear correlation between the two asset categories over 2017-2024 since all 4 assets show an increasing trend.
+Therefore, to represent this relationship, I will choose a linear regression model.
 
@@
 
-Define $y$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_b$ as the Bitcoin price and $y_e$ as the Ethereum price. Then $x_g$ and $x_s$ will be the price of gold and silver respectively.
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+$$
+y_e + y_b =  b_0 + b_1(x_g + x_s) + c
+$$
+This can be simplified if the metals were aggregated into $y_i = y_e + y_b$ and $x_i = x_g + x_s$.
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+$$
+y_i = b_0 + b_1x_i + c
+$$
+Where:
 
-### Model justification
+-   $y_i$ is the aggregated representation of the prices of the two major cryptocurrencies
+-   $x_i$ is the aggregated representation of the prices of the two major precious metals
+-   $b_0$ is the intercept where the price of the precious metals would be equal to zero
+-   $b_1$ is the slope coefficient/estimated rate of change for cryptos for every one unit of change for metals
+-   $c$ is the error variable that accounts for deviations from the predicted value
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
+### Model Justification
+I expect there to be a positive correlation between
 
 # Results
-
-Our results are summarized in @tbl-modelresults.
-
 ```{r}
@@
 
-first_model <-
-  readRDS(file = here::here("models/price chart.rds"))
-```
-
-```{r}
+first_model <- readRDS(file = here::here("models/volatility chart.rds"))
 
@@
 
+## Price Results
+
+## Volatility Results
+
+Our results are summarized in...
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-3s
+#| fig-cap: "Volatility Chart"
+
+first_model
+```
+The Volatility chart shows that
+
+{{< pagebreak >}}
 # Discussion
 
-##
+## Precious Metals As An Investment
+As the world enters a recession, we can confidently look at historical data for precious metals near and far and identify that it would do well to hold its value and steadily rise through economic failures and inflation.
+As shown in @fig-1, precious metals, especially gold is almost unaffected by the recession caused by Covid-19.
+In addition, @fig-2 demonstrates that the normalized average true range values for precious metals tend to be significantly lower than that of cryptocurrencies.
+That is suggestive that precious metals are stable investments and can be treated as very stable investments.
+As my previous models predict, precious metals will continue to increase in value in the future.
+As an investor, if you are looking to invest in precious metals the two most common options will be to either invest in derivative contracts or through gold mutual funds [@InvestopediaInv].
+The second option would be to buy the physical metals in the form of coins or bars, however, this method is much more difficult to keep track of and lack mobility.
+Overall, precious metals is a great investment to dedicate to for those who wants to hedge against inflation, diversify their portfolio, while maintaining stability.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Cryptocurrencies As An Investment
+Cryptocurrencies is the new wave.
+Aside from Bitcoin and Ethereum, we are have seen the rise of many other successful cryptocurrencies such as Monero, Litecoin, and Stellar Lumens just to name a few.
+@fig-1 can attest to the substantial growth of cryptocurrencies over the last decade.
+However, @fig-2 shows that even though Bitcoin and Ethereum has been extremely profitable, they are both extremely volatile assets with normalized average true range values over 5 times that of precious metals.
+As an investor, cryptocurrencies can be much more appealing, especially towards the newer crowd.
+Investing in crypto is much more straightforward than precious metals.
+With large crypto exchanges such as Coinbase, Binance, and Kraken gaining popularity buying crypto has never been easier.
+Moreover, crypto wallets can come in the form of a USB Ledger or even an app on the appstore.
+This makes the asset extremely lightweight and mobile.
 
-## Second discussion point
+## Different Stroke For Different Folks
+Both cryptocurrencies and precious metals are amazing investments.Throughout my analysis, I have concluded that there is a correlation between the two category of assets, both assets have seen massive growth, and both still have a lot of room to develop in the future.
+For the readers still asking: Which asset should I invest in?
+I believe the answer is this:
+
+For those who are looking for something long term to hold onto.
+For those who want to sit on an asset for medium to long term, precious metals is the better investment.
+Whether you would want to buy futures, or invest in mutual funds, go for precious metals.
+This process will involve more time in effort whether it's purchasing or liquidating.
+Opening a mutual fund or dealing with derivative contracts is not simple and will take days to attain.
+Similarly, purchasing, carrying, and selling physical metals is also a tedious task.
+The result however, will be a long term investment that is stable and profitable.
+
+For those who are looking for something long or short term, and that are more risk-seeking, cryptocurrencies will be your cup of tea.
+Though seemingly much more profitable in the recent years, these assets are much more volatile and is very dependent on economic climate.
+Moreover, compared to precious metals, buying, storing, and selling is a breeze.
+In cryptocurrencies is an asset with very high potential ceiling and as blockchain technology continues to progress, cryptocurrencies have a very bright future.
 
@@
 ## Next Steps
-Some next steps I can take for future devlopments can be to continue to monitor the price of crypto over the next few decades and see how it reacts to different economic coniditions and how that compares to precious metals.
+Some next steps I can take for future developments can be to continue to monitor the price of crypto over the next few decades and see how it reacts to different economic conditions and how that compares to precious metals.
 
-\newpage
+## Closing Remarks
+Before investing in anything, nothing beats your own research. An investment should be considered only after sufficient self evaluation. Ask yourself:
 
-\appendix
+-   How much money am I looking to invest?
 
-# Appendix {-}
+-   What is my tolerance for risk?
 
-# Additional data details
+-   What are my investment goals and objectives?
 
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-
-```
+I have given but a brief overview an analyses of two popular modern day assets. The rest is up for you to discover.
 

### 2024-04-17 scripts/04-model.R

@@ -79,7 +79,11 @@ egplot <- ggplot(price_join, aes(x = eth_Close, y = gold_Close)) +
 print(egplot)
 
 # Regression for Ethereum-Silver
-esfit <- lm(silver_Close ~ eth_Close, data = price_join)
+esfit <- stan_glm(
+  formula = silver_Close ~ eth_Close,
+  data = price_join,
+  family = gaussian()
+)
 esplot <- ggplot(price_join, aes(x = eth_Close, y = silver_Close)) +
   geom_point(color = "blue", size = 2) +
   geom_abline(intercept = coef(esfit)[1], slope = coef(esfit)[2], color = "red") +

### 2024-04-18 paper/paper.qmd
Finished Paper

@@
 __________
-Then the average true range was calculated with and represented by (asset)_ATR in @tbl-3:
+Then the average true range was calculated with and represented by (asset)_ATR in @fig-1:
 
@@
 __________
-In the final step, the normalized average true range was calculated by normalizing the ATR value with the closing price of the asset and represented by (asset)_ATR_norm in @tbl-3:
+In the final step, the normalized average true range was calculated by normalizing the ATR value with the closing price of the asset and represented by (asset)_ATR_norm in @fig-1:
 
@@
 
-### Model Justification
-I expect there to be a positive correlation between
+## Model Justification
+Both precious metals and cryptocurrencies have been used historically as a way to hedge against inflation, so when the economy doesn't do well, investors look to buy up these assets as a way to preserve the value of their cash.
+Furthermore, these assets follow a similar integrity where they are mined, either digitally or physically, and there is a decreasing supply it the more they are mined.
+Considering all factors aforementioned, a linear regression model is a reasonable framework for assessing the relationship between the two assets.
 
+{{< pagebreak >}}
 # Results
@@
 #| echo: false
-#| eval: true
 #| warning: false
 #| message: false
+#| include: false
 
 library(rstanarm)
+crypto$totalc <- crypto$eth_Close + crypto$btc_Close
+metals$totalm <- metals$gold_Close + metals$silver_Close
+price_join <- merge(crypto, metals, by = "Date", all = FALSE)
+price_join <- select(price_join, Date, totalc, totalm)
+first_model <- readRDS(file = here::here("models/volatility chart.rds"))
+esfit <- stan_glm(
+  formula = totalc ~ totalm,
+  data = price_join,
+  family = gaussian()
+)
 
-first_model <- readRDS(file = here::here("models/volatility chart.rds"))
+reg <- ggplot(price_join, aes(x = totalm, y = totalc)) +
+  geom_point(color = "blue", size = 2) +
+  geom_abline(intercept = coef(esfit)[1], slope = coef(esfit)[2], color = "red") +
+  labs(title = "Crypto vs. Metals Prices Regression Model",
+       x = "Metals Closing Price", y = "Cryptos Closing Price")
 
@@
 
-## Volatility Results
+```{r}
+#| label: fig-2
+#| fig-cap: "Model showing relationship between metals prices and crypto prices"
+#| echo: false
+#| warning: false
 
-Our results are summarized in...
+reg
+```
+
+@fig-2 suggests that the prices of aggregated metals (gold and silver) and that of aggregated cryptos (Bitcoin and Ethereum) have a positive and strong relationship.
+This is reinforced when observing the summary data below.
+There is a positive coefficient at 1.6 for totalm (aggregated metals).
+In other words, as the price of the aggregated metals increase by 1 unit, the model predicts an increase in aggregated crypto by 1.6 units on average.
+The correlation analysis concludes an r value of ~0.71.
+The aforementioned information suggest a moderately strong and positive relationship between precious metals aggregate price and crypto aggregate prices.
+Though there is a positive correlation between the price factors of these asset categories, there is no implication of causation.
 
@@
 #| warning: false
-#| label: fig-3s
-#| fig-cap: "Volatility Chart"
+#| fig-cap: "Summary Data for Regression Model"
+
+esfit
+"__________________________"
+"Correlation:"
+correlation <- cor(price_join$totalm, price_join$totalc)
+correlation
+```
+
+## Volatility Results
+
+The volatility results strongly suggests that cryptocurrencies are much more unstable compared to precious metals.
+I use normalized average true range as a measure because it takes the average range between high and low prices over a specific period.
+Higher ATR values suggest higher volatility because there is a greater shift in prices.
+The normalized ATR is the ATR normalized over the closing price of that day as a way to balance and fairly judge the ATR of the four individual assets.
+@fig-3 shows evidently that the normal ATR values of Bitcoin and Ethereum dwarfs those of gold and silver.
+Gold is the most consistent with a normalized ATR resting consistently at 0.01, silver is the second most stable coming in at around 0.02.
+The two cryptocurrencies see way higher normalized ATR values I would estimate to be around 0.05 on average and a much more turbulent trend line.
+This data is congruent with our price chart @fig-1 where gold had the most stable price rise followed by silver and then the cryptos.
+Because the normalized ATR for the cryptocurrencies are many times higher than that of precious metals, we can assume that they are also significantly more volatile.
+
+```{r}
+#| echo: false
+#| warning: false
+#| label: fig-3
+#| fig-cap: "Volatility Chart Observed Through Normalized Average True Range"
 
@@
 ```
-The Volatility chart shows that
 
@@
 Aside from Bitcoin and Ethereum, we are have seen the rise of many other successful cryptocurrencies such as Monero, Litecoin, and Stellar Lumens just to name a few.
-@fig-1 can attest to the substantial growth of cryptocurrencies over the last decade.
-However, @fig-2 shows that even though Bitcoin and Ethereum has been extremely profitable, they are both extremely volatile assets with normalized average true range values over 5 times that of precious metals.
-As an investor, cryptocurrencies can be much more appealing, especially towards the newer crowd.
-Investing in crypto is much more straightforward than precious metals.
+@fig-1 can attest to the substantial growth of cryptocurrencies over the last decade: Bitcoin grew from 7,000 USD to almost 70,000 USD in the span of less than 7 years.
+Ethereum grew from around 330 USD to over 3500 USD.
+10x of an investment over less than 7 years is sensationally high retruns.
+However, @fig-3 shows that even though Bitcoin and Ethereum has been extremely profitable, they are both extremely volatile assets with normalized average true range values many times that of precious metals.
+Due to the extreme volatility of cryptos, many begin looking at crypto as assets for day trading or short term options.
+As an investor, cryptocurrencies can be much more appealing, especially towards the newer crowd because investing in crypto is much more straightforward than precious metals.
 With large crypto exchanges such as Coinbase, Binance, and Kraken gaining popularity buying crypto has never been easier.
@@
 ## Different Stroke For Different Folks
-Both cryptocurrencies and precious metals are amazing investments.Throughout my analysis, I have concluded that there is a correlation between the two category of assets, both assets have seen massive growth, and both still have a lot of room to develop in the future.
+Both cryptocurrencies and precious metals are amazing investments.Throughout my analysis, I have concluded that there is a strong positive relationship between the two category of assets, both assets have seen massive growth, and both still have a lot of room to develop in the future.
 For the readers still asking: Which asset should I invest in?
@@
 Though seemingly much more profitable in the recent years, these assets are much more volatile and is very dependent on economic climate.
-Moreover, compared to precious metals, buying, storing, and selling is a breeze.
-In cryptocurrencies is an asset with very high potential ceiling and as blockchain technology continues to progress, cryptocurrencies have a very bright future.
+Movements such as currencies being delisted from major exchanges or countries enforcing crypto laws can result in massive movements and potentially even the downfall of a cryptocurrency.
+This potentially tumultuous investment will take significantly more effort when it comes to monitoring activity and making adjustments.
+However, compared to precious metals, buying, storing, and selling is a breeze.
+Cryptocurrencies are assets with a very high potential ceiling and as blockchain technology continues to progress, cryptocurrencies have a very bright future.
 
 ## Biases and Weaknesses
-One of the greatest weaknesses stems from the limited historical data of cryptocurrencies.
-The value of precious metals can be trace back centuries and has solidified itself as a solid holding asset while cryptocurrencies such as Ethereum was only introduced in the late 2016s.
-Therefore, the only results and conclusion that can be made...
+The potential bias in my analysis comes from data recording errors from yahoo finance.
+However, that should be pretty minimal.
+Another potential bias could result from selection bias that occurs in my data cleaning.
+I chose to only take the first and fifteenth day of every month when creating my price charts and Normal ATR charts.
+Though said selection process can help reduce noise and ignore short term variations, I could very well have missed out on certain trends that occur on the days between.
+Aside from data biases, one incorrect assumption could be that the relationship between crypto and precious metals is linear.
+In many instances from the price chart @fig-1, there seem to be exponential growth from crypto compared to linear grown from metals and this is observed again in @fig-2 where there is a slight curve in the points suggesting potential a exponential regression model.
+
+One of the greatest weaknesses in my analysis stems from the limited historical data of cryptocurrencies.
+The value of precious metals can be trace back a century ago and has solidified itself as a strong holding asset while cryptocurrencies such as Ethereum was only introduced in the late 2017s.
+As a relatively immature market paired with easy influence from outside factors such as technological advancements and crypto laws, there are too many qualitative aspects that need to be accounted for but my analysis can only give a quantitative prediction based on historical prices.
 
 ## Next Steps
-Some next steps I can take for future developments can be to continue to monitor the price of crypto over the next few decades and see how it reacts to different economic conditions and how that compares to precious metals.
+Some next steps I can take for future developments can be to continue to monitor the price of crypto over the next few decades and see how it reacts to different economic patterns and how that compares to precious metals.
+Moreover, I can include more assets in my comparisons such as technology stocks or real estate.
+The overall next step for improving this analysis is to increase the amount of factors
 
 ## Closing Remarks
-Before investing in anything, nothing beats your own research. An investment should be considered only after sufficient self evaluation. Ask yourself:
+Before investing in anything, nothing beats individual research. An investment should be considered only after sufficient self evaluations.
+
+Ask yourself:
 
@@
 
-I have given but a brief overview an analyses of two popular modern day assets. The rest is up for you to discover.
+I have given but a brief overview and analyses of two popular modern day assets. The rest is up for you to discover.
 

### 2024-04-18 scripts/04-model.R

@@ -17,7 +17,6 @@ metals <- read_csv(here::here("data/analysis_data/metals prices.csv"))
 cryptov <- read_csv(here::here("data/analysis_data/crypto volatility.csv"))
 metalsv <- read_csv(here::here("data/analysis_data/metals volatility.csv"))
 
-price_join <- merge(crypto, metals, by = "Date", all = FALSE)
 
 
 ### Model data ####
@@ -35,8 +34,6 @@ compilation <- ggplot() +
   guides(color = guide_legend(title = "Assets")) +  
   scale_x_date(date_breaks = "1 year", date_labels = "%Y")
 
-compilation
-
 # Volatility Data Chart
 volatility <- ggplot() +
   geom_line(data = cryptov, aes(x = Date, y = eth_ATR_norm, color = "Ethereum"), size = 0.75) +
@@ -49,47 +46,23 @@ volatility <- ggplot() +
   guides(color = guide_legend(title = "Assets")) +  
   scale_x_date(date_breaks = "1 year", date_labels = "%Y")
 
-volatility
+# Regression Chart Metals and Crypto
+crypto$totalc <- crypto$eth_Close + crypto$btc_Close
+metals$totalm <- metals$gold_Close + metals$silver_Close
+price_join <- merge(crypto, metals, by = "Date", all = FALSE)
+price_join <- select(price_join, Date, totalc, totalm)
 
-# Regression Chart BTC-Gold
-bgfit <- lm(gold_Close ~ btc_Close, data = price_join)
-bgplot <- ggplot(price_join, aes(x = btc_Close, y = gold_Close)) +
-  geom_point(color = "blue", size = 2) +
-  geom_abline(intercept = coef(bgfit)[1], slope = coef(bgfit)[2], color = "red") +
-  labs(title = "Bitcoin vs. Gold Prices Regression Model",
-       x = "Bitcoin Closing Price", y = "Gold Closing Price")
-print(bgplot)
-
-# Regression for BTc-Silver
-bsfit <- lm(silver_Close ~ btc_Close, data = price_join)
-bsplot <- ggplot(price_join, aes(x = btc_Close, y = silver_Close)) +
-  geom_point(color = "blue", size = 2) +
-  geom_abline(intercept = coef(bsfit)[1], slope = coef(bsfit)[2], color = "red") +
-  labs(title = "Bitcoin vs. Silver Prices Regression Model",
[…]
